\includegraphics[width=1.0\textwidth]{SimAUDLogo.png}\\\quad\\A Three-Tier Architecture Visual-Programming Platform for Building-Lifecycle Data Management

### 2020-03-30 paper_LateX/main.tex

\begin{abstract}
	In this paper, we present a platform that integrates three main aspects in the building industry: 1) Building data from both IoT devices and Building Management System (BMS), 2) Building Energy modeling and simulation engine, and 3)Data analysis and optimization libraries. All of which are combined in a three-tier architecture cloud platform. The platform aims to provide useful representations of the data to different stakeholders. We defined three main types of stakeholders. Each stakeholder uses the platform differently: (1) End-use programmers, who use visual programming and textual programming interfaces to perform computational tasks, (2) Dashboard viewers who are interested in viewing insightful real-time data about performance in the form of charts and diagrams, and (3) Data feedback inputters such as occupants to give feedback or fill questionnaires. The three-tier architecture enables the spatial and physical separation of the databases, the computational engines, and the user-interfaces. This separation resulted in some advantages such as flexibility, scalability (horizontal and vertical), reusability, and latency reduction. \hl{Currently, the platform is in the final stage of development. The following stage includes community testing and user experience enhancement.}
\end{abstract}

@@

\begin{figure*}[h]
\centering
\includegraphics[width=\linewidth]{imgs/platform_interface.png}
\caption{The main interface functions}
\label{fig:platformInterface}
\end{figure*}

@@

\underline{Description: }
\begin{enumerate}
    \item EnergyModeller starts a new definition (project).
    \item The IDF file link and global unique id (GUID) are retrieved. 
    \item EnergyModeller uploads the IDF file to the data layer (a scalable google cloud bucket) using a file upload component (Figure \ref{fig:fileupload_comp}) -- an animated GIF image could be viewed \href{https://user-images.githubusercontent.com/6969514/77833649-16c24280-717a-11ea-9df1-8a5e0f7bae83.gif}{here}.

    \item EnergyModeller loads a "buildSimHub Parametric Study" component (Figure \ref{fig:parametric_study}). 
    \item fsdfsafasdf
    \item fsdfsafasdf
    \item fsdfsafasdf
\end{enumerate}

@@

@@

@@

\section*{ACKNOWLEDGMENTS}
% This paper is a part of a project funded by the Ng Teng Fong Charitable Foundation (NTFCF) research funding.
% \clearpage
% \balance

>>>>

\begin{abstract}
	In this paper, we present a platform that integrates three main aspects in the building industry: 1) Building data from both IoT devices and Building Management System (BMS), 2) Building Energy modeling and simulation engine, and 3)Data analysis and optimization libraries. All of which are combined in a three-tier architecture cloud platform. The platform aims to provide useful representations of the data to different stakeholders. We defined three main types of stakeholders. Each stakeholder uses the platform differently: (1) End-use programmers, who use visual programming and textual programming interfaces to perform computational tasks, (2) Dashboard viewers who are interested in viewing insightful real-time data about performance in the form of charts and diagrams, and (3) Data feedback inputters such as occupants to give feedback or fill questionnaires. The three-tier architecture enables the spatial and physical separation of the databases, the computational engines, and the user-interfaces. This separation resulted in some advantages such as flexibility, scalability (horizontal and vertical), reusability, and latency reduction. Currently, the platform is in the final stage of the alpha release development. The following stage includes community testing and user experience enhancement.
\end{abstract}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{imgs/platform_interface.png}
\caption{The main interface functions}
\label{fig:platformInterface}
\end{figure}

@@

\textbf{\underline{Description: }}
\begin{enumerate}
    \item EnergyModeller starts a new definition -- (Tier1 - presentation layer).
    \item In the presentation layer, the EnergyModeller uploads the IDF file to the data layer (Tier 3) which is a scalable google cloud bucket using a file upload component (Figure \ref{fig:fileupload_comp}). This step takes place through the application layer (Tier2) which contains a Google Cloud Storage application programming interface (API) and other file validation and security checks -- an animated GIF image could be viewed \href{https://user-images.githubusercontent.com/6969514/77833649-16c24280-717a-11ea-9df1-8a5e0f7bae83.gif}{here}.
    \item The IDF file link and global unique id (GUID) are retrieved. 
    \item EnergyModeller loads a "buildSimHub Parametric Study" component (Figure \ref{fig:parametric_study}). 
    \item After running the component, a request is sent to the simulation engine in the application layer including the inputs (IDF file, project api key, and the simulation parameters). 
    \item The output of the simulation comes in a form of JavaScript Object Notation (JSON) as well as a chart (Figure \ref{fig:plot_panel}) -- a full view of the project can be downloaded \href{https://user-images.githubusercontent.com/6969514/77868854-2ff8eb00-726f-11ea-837d-efedac7a80a5.png}{ here}. 
\end{enumerate}

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{paper_LateX/imgs/bsh_param.png}
\caption{ Parametric simulation study: this component runs a cloud simulation engine in the application layer. The inputs are: (1) The project\_api\_key, i.e. a unique id for each simulation project, and is used to track the project and run different simulation models' progress; (2) file\_dir: which is the IDF file stored in the data layer (tier 3) in the form of a flat file; (3) The simulation parameters. After running the component, the outputs (4) come in the form of JavaScript Object Notation (JSON) object and a plot which can be displayed in a panel (Figure \ref{fig:plot_panel}) and embedded in a website.}
\label{fig:parametric_study}
\end{figure}

\begin{figure}[h]
\includegraphics[width=\columnwidth]{paper_LateX/imgs/display_data_plot_json.png}
\caption{ Display results as a chart and/or JSON tree in the presentation layer.}
\label{fig:plot_panel}
\end{figure}

@@

\textbf{Currently, the platform still in the final stages of developing and debugging the alpha release. The platform will be released as an open source and contributions are welcome from the community. Contribution instructions will be available on the following GitHub repository}:

\href{https://github.com/ideas-lab-nus/paper-SIMAUD2020-three-tier-architecture-platform}{https://github.com/ideas-lab-nus/paper-SIMAUD2020-three-tier-architecture-platform}

@@

\section*{ACKNOWLEDGMENTS}
This paper is a part of a project funded by the Ng Teng Fong Charitable Foundation (NTFCF) research funding.

\balance
